MixEth: efficient trustless coin mixing service for Ethereum

### 2018-11-03 article/main.tex
Proof of recipient anonymity added

\subsubsection{Anonymity}
\textit{Sender} anonymity is achieved if an adversary can not determine to whom honest senders are sending funds, assuming that honest senders' deposits are indistinguishable.

@@

\subsubsection{Availability}
It is essential for a coin mixer to provide availability, meaning that honest recipients can always withdraw their money from the mixer.
\subsubsection{Theft prevention}
We would like to ensure that neither coins can be withdrawn twice, nor withdrawn by anyone other but the intended recipient. 
\section{MixEth}

@@

\begin{table}[H] 
	\caption{Preliminary implementation gas cost results. Expect further improvements. MixEth++ refers to the implementation which leverages state channels for shuffling and challenging periods}
	\centering 
	\begin{tabular}{@{\extracolsep{6pt}}lcccc@{}}

		\toprule
		\hline
		&Deposit&\multicolumn{2}{c}{Shuffle}& Withdraw\\
		\cline{3-4}&&Shuffle upload&Challenge\\
		\hline
		\midrule
		Möbius \cite{meiklejohn2018mobius}     &$\num[group-separator={,}]{76123}$&0&0&$\num[group-separator={,}]{335714}$n   \\
		Miximus \cite{miximus2018}&$\num[group-separator={,}]{732815}$&0&0 &$\num[group-separator={,}]{1903305}$  \\
		MixEth&\num[group-separator={,}]{99254}&\num[group-separator={,}]{153268}+\num[group-separator={,}]{40000}n&\num[group-separator={,}]{210220}&\num[group-separator={,}]{113265}  \\
		MixEth++&TBD&0&0&TBD\\
		\bottomrule
	\end{tabular}
	\label{table:securityproperties}
\end{table}

@@

\section{Proof of Anonymity}
Reduction to DDH has to be added here

\begin{bbrenv}{A}
 \begin{bbrbox} [name=BoxName]
 \pseudocode {
	 \text{ s t e p 1} \\
	 \text{ s t e p 2} \\
	 \pcfor\text{some c o n d i t i o n } \pcdo \\
	 \pcind\text{step3}
	 }

 \begin{bbrenv}{B}
 \begin{bbrbox}[name=InnerBox]
 \pseudocode{
	 \text{ i n n e r s t e p 1} \\
	 \text{ i n n e r s t e p 2} \\
	 }
 \end{bbrbox}
 \end{bbrenv}

 \pseudocode{
	 \text{ s t e p 4} \\
	 \text{ s t e p 5} \\
	 }
 \end{bbrbox}
 \bbrinput{input}
 \bbroutput{output}
 \end{bbrenv}

>>>>

\subsubsection{Anonymity} \label{sec:defanonymity}
\textit{Sender} anonymity is achieved if an adversary can not determine to whom honest senders are sending funds, assuming that honest senders' deposits are indistinguishable.

@@

\subsubsection{Availability}
It is essential for a coin mixer to provide availability, meaning that honest recipients can always withdraw their money from the mixer.

\subsubsection{Theft prevention}
We would like to ensure that neither coins can be withdrawn twice, nor withdrawn by anyone other but the intended recipient. 
\section{MixEth}

@@

\begin{table}[H] 
	\caption{Preliminary implementation gas cost results. Expect further improvements. MixEth++ refers to the implementation which leverages state channels for shuffling and challenging periods}
	\centering 
	\begin{tabular}{@{\extracolsep{6pt}}lccccc@{}}

		\toprule
		\hline
		&Deployment&Deposit&\multicolumn{2}{c}{Shuffle}& Withdraw\\
		\cline{4-5}&&&Shuffle upload&Challenge\\
		\hline
		\midrule
		Möbius \cite{meiklejohn2018mobius}     &$\num[group-separator={,}]{1046027}$&$\num[group-separator={,}]{76123}$&0&0&$\num[group-separator={,}]{335714}$n   \\
		Miximus \cite{miximus2018}&$\num[group-separator={,}]{1751378}$&$\num[group-separator={,}]{732815}$&0&0 &$\num[group-separator={,}]{1903305}$  \\
		MixEth&TBD&\num[group-separator={,}]{99254}&\num[group-separator={,}]{138653}+\num[group-separator={,}]{40000}n&\num[group-separator={,}]{210220}&\num[group-separator={,}]{113265}  \\
		MixEth++&TBD&TBD&0&0&TBD\\
		\bottomrule
	\end{tabular}
	\label{table:securityproperties}
\end{table}

@@

\section{Proof of Anonymity}
Hereby we show that if there exists an adversary $\adv$ who is able to break withdrawal anonymity defined in~\ref{sec:defanonymity}, then there exists another adversary $\bdv$ who is able to break the DDH assumption.

\begin{wrapfigure}{r}{0.5\textwidth}
	\centering
\begin{bbrenv}{A}
 \begin{bbrbox} [name=\bdv]
 \pseudocode {
	 \text{$\textsf{PK}_{B} = (s_{0}C^{*}, s_{1}C^{*})$} \\
	 \text{$tx \stackrel{\$}{\leftarrow}Withdraw(tumblers[j],sk_{B_{l_{b}}})$}
	 }

 \begin{bbrenv}{B}
 \begin{bbrbox}[name=\adv]
 \pseudocode{
 	 \text{Input: $PK_{B}, tx$} \\
	 \text{Output: $b^'$} \\
	 }
 \end{bbrbox}

 \end{bbrenv}

 \end{bbrbox}

 \bbrinput{$(s_{0}G,C^{*},s_{b}C^{*})$}
 \bbroutput{$b^'$}
\end{bbrenv}

\captionof{figure}{An illustration for the reduction of withdrawal anonymity to the DDH assumption}
\end{wrapfigure}

Let us assume that the challenge to the DDH-adversary $\bdv$ is of the form $(s_{0}G,C^{*},s_{b}C^{*})$. If original keys are $(s_{0}G, s_{1}G)$ and shuffled keys are $\textsf{PK}_{B}=(s_{0}C^{*}, s_{1}C^{*})$, then $\bdv$ forwards $\textsf{PK}_{B}$ to $\adv$. Then a withdrawal transaction occurs from $s_{b}C^{*}$. After polynomial-time $\adv$ outputs $b^{'}$ and $\bdv$ will outpu the very same bit. It is straightforward to see that $\bdv$ wins the DDH-game if and only if $\adv$ wins the $\textsf{G}^{with, anon}_{mix, \adv}$ security game. Therefore, by the assumption that recipient anonymity does not hold we have that $$\textsf{non-negl}(\lambda)=\Pr[\textsf{G}^{with, anon}_{mix, \adv}]=\Pr[\textsf{DDH}_{\bdv}],$$ which contradicts to the DDH assumption.
